04-Figure5b

### 2021-05-27 notebooks/04-Fig5b-052721.Rmd
update on calculating effector name intersections

>>>>

prs_column$tolist  <-  str_remove_all(prs_column$study_items,'\\[|\\]')%>%
  #str_split(.,', ')%>%
  str_extract_all(.,"[^',]+[^']")# %>%list()

df <- data.frame(matrix(ncol = 2, nrow = 0))
colnames(df) <- c("orf_name_id", "count")
for(i in unique(prs_column$orf_name_id)){
  all_set = unlist(prs_column$tolist[prs_column$orf_name_id==i])
  int_ <- length(intersect(all_set,effector_pcc$`Systematic gene name`))
  df <- bind_rows(df,data.frame(orf_name_id=i,count=int_))
}
num_of_groups_with_effectors <- df%>%filter(count>0)%>%nrow()
